#### Compare performance of the original function against the updated version

```{r message=FALSE}
library(tidyverse)
library(microbenchmark)
library(lubridate)
library(compareDF)
library(reshape2)
library(kableExtra)
source("parse_GHCN_data.R")
source("parse_GHCN_data_orig.R")
```

##### Check outputs
The outputs of the two functions differ slightly, so do a quick check to make sure that they can systematically be made equivalent for comparison:
```{r error=TRUE}

compare_versions <- compare_df(df_old = parse_GHCN_data("CA004010358.dly") %>%
                                 mutate(across(.cols = c("year", "month", "value"),
                                               .f = as.integer),
                                        across(.cols = where(is.character),
                                               .f = trimws)),
                               df_new = parse_GHCN_data_new("CA004010358.dly") %>%
                                 mutate(day = as.integer(day)),
                               group_col = c("station", "year", "month", "variable", "day", "date"))

```
The original function leaves in whitespace where there are (purposeful) blanks, whereas the updated version running on `read_fwf` does not. Also needed to match up columns that are integer class.

##### Check speed
Ok, now compare the speeds both as-is, and with the corrections needed for equivalence
```{r}
# Compare process of making basic outputs for each
basic <- microbenchmark(orig = parse_GHCN_data("CA004010358.dly"),
                        updated = parse_GHCN_data_new("CA004010358.dly"),
                        times = 100)
```

```{r echo=FALSE}
summary(basic) %>% kbl() %>% kable_paper()

```

```{r}
# Compare process of making making identical outputs for each
matched <- microbenchmark(orig = parse_GHCN_data("CA004010358.dly") %>%
                            mutate(across(.cols = c("year", "month", "value"),
                                          .f = as.integer),
                                   across(.cols = where(is.character), .f = trimws)),
                          updated = parse_GHCN_data_new("CA004010358.dly") %>%
                            mutate(day = as.integer(day)) %>%
                            arrange(date),
                          times = 100)
```

```{r echo=FALSE}
summary(matched) %>% kbl() %>% kable_paper()
```
